### 2019-10-27 report/implementation.tex
Rework some sentences and notations

We decided to implement the last paper to compute Wasserstein distances on images in a efficient way. We then use convolutional Sinkhorn in SVM as Marco Cuturi used Sinkhorn in his paper to classify images of the MNIST digit database \cite{Cut}. The implementation of the convolutional Wassertein distance has been written in C++. We then write the Gramm matrix of a subset of the MNIST database in a file and use it in a Python script to use SVM from Sklearn library.

\paragraph{How to use our code}
OpenMP has been used to parallelize the code. If you don't have OpenMP already install, you can install it with \verb|sudo apt install libomp-dev|.
To compile the C++ code you just have to type \verb|make|. Then you need to obtain the train image datatset and the train label dataset of the MNIST database \url{http://yann.lecun.com/exdb/mnist/}. To do so you have to run the script \verb|get_mnist.sh| which will download and rename the files correctly. The executable \verb|main| created by \verb|make| command can be used in four ways.
\begin{itemize}
	\item  \verb|./main bar| to reproduce an image similar to the \figurename~\ref{barp}; An image containing different barycenters of four shapes.
	\item \verb|./main card| to reproduce images similar to the \figurename~\ref{cardp}; An interpolation of two images of cards.
	\item \verb|./main wass > kernel.txt| to compute a kernel with the convolutional Wasserstein distance of \verb|N_TRAIN| images of the MNIST dataset. We project \verb|N_TEST| other digit images of the MNIST dataset on the kernel space created. You can change the parameter \verb|N_TRAIN| and \verb|N_TEST| at the beginning of the file \verb|src/main.cpp|. The kernel will then be written if the file \verb|kernel.txt|.
	\item \verb|./main eucl > kernel.txt| to do the same as the previous command but with Euclidean distance instead of Wasserstein distance. 
\end{itemize}
Finally when a kernel file is computed you can test SVM on it thanks to the python script \verb|learning.py|. Because computing Wasserstein kernel may take a while we provide the Wasserstein kernel \verb|kernels/wass.txt| and the Euclidean kernel \verb|kernels/eucl.txt|. You can then run:
\begin{center}
	\verb=python3 learning.py < [kernels/wass.txt | kernels/eucl.txt]=
\end{center}
It will print the performances of these two kernels, show the projection of the data on the two principle components and finally show the kernel matrix.

>>>>

We decided to implement the last paper to compute Wasserstein distances
on images in an efficient way. We then use convolutional Sinkhorn in an SVM
classifier as Marco Cuturi used Sinkhorn in his paper to classify images of
the MNIST digit database \cite{Cut}. The implementation of the convolutional
Wassertein distance has been written in C++. We then write the Gramm matrix
of a subset of the MNIST database in a file and use it in a Python script
to use SVM from Sklearn library.

\paragraph{How to use our code}
OpenMP has been used to parallelize the code. If you don't have OpenMP already
installed, you can install it with \verb|sudo apt install libomp-dev|.
To compile the C++ code you just have to type \verb|make|. Then you need
to obtain the train image datatset and the train label dataset of the MNIST
database \url{http://yann.lecun.com/exdb/mnist/}. To do so you have to run
the script \verb|get_mnist.sh| which will download and rename the files
correctly. The executable \verb|main| created by \verb|make| command can be
used in four ways.

\begin{itemize}
	\item  \verb|./main bar| to reproduce an image similar to the
	\figurename~\ref{barp}; An image containing different barycenters
	of four shapes.

	\item \verb|./main card| to reproduce images similar to the
	\figurename~\ref{cardp}; An interpolation of two images of cards.

	\item \verb|./main wass > kernel.txt| to compute a kernel with
	the convolutional Wasserstein distance of \verb|N_TRAIN| images of
	the MNIST dataset. We project \verb|N_TEST| other digit images of
	the MNIST dataset on the kernel space created. You can change the
	parameter \verb|N_TRAIN| and \verb|N_TEST| at the beginning of the
	file \verb|src/main.cpp|. The kernel will then be written if the
	file \verb|kernel.txt|.

	\item \verb|./main eucl > kernel.txt| to do the same as the previous
	command but with Euclidean distance instead of Wasserstein distance.
\end{itemize}
Finally when a kernel file is computed you can test SVM on it
thanks to the python script \verb|learning.py|. Because computing
Wasserstein kernel may take a while to compute we provide a pre-computed
Wasserstein kernel \verb|kernels/wass.txt| as well as an Euclidean kernel
\verb|kernels/eucl.txt|. You can then run:
\begin{center}
	\verb=python3 learning.py < [kernels/wass.txt | kernels/eucl.txt]=
\end{center}
It will print the performances of these two kernels, show the projection of
the data on the two principle components and finally show the kernel matrix.
